---
title: "README"
author: "Bob Rudis"
date: "August 10, 2014"
output:
  md_document:
    variant: markdown_github
---

Version 1.1 brings a significant update to the core components of the `netinel` package. Every function has been re-written to be as fast as possible without resorting to `Rcpp` functions.

Current function list:

- `Alien.Vault.Reputation` - Retrieves Alien Vault's IP reputation database
- `BulkOrigin` - Retrieves BGP Origin ASN info for a list of IPv4 addresses
- `BulkOriginASN` - Retrieves BGP Origin ASN info for a list of ASN ids
- `BulkPeer` - Retrieves BGP Peer ASN info for a list of IPv4 addresses
- `CIRCL.BGP.Rank` - Retrieves CIRCL aggregated, historical/current BGP rank data
- `SANS.ASN.Detail` - Retrieves SANS ASN intel currently tracked IP detail

### Installation

```{r eval=FALSE}
library(netintel)
```

### Usage

```{r}
library(netintel)

# current verison
packageVersion("netintel")


```

### Test Results

```{r}
library(netintel)
library(testthat)

date()

test_dir("tests/")

```
